Article Title

### 2019-11-20 Paper.tex
Add mapping feature to cleanup

Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a \emph{gold standard} consisting of annotations that are assumed to be correct.
We used annotations that were created or in some way curated with human participation for gold standards.
There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
In the meantime, \citet{Plyusnin2018} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
\texttt{TODO\ DESCRIBE\ THEIR\ APPROACH}
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in \texttt{TODO}.

@@

\rowcolor{gray!6}   & GoldStandard-OFF & 1 & 0 & 0\\

@@

\rowcolor{gray!6}   &  & GoldStandard-OFF & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\

@@

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.384973 & 0.346840 & 0.191962 & 0.004446 & 0.006115 & 0.004811\\
\cmidrule{1-8}
 & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a \emph{gold standard} consisting of annotations that are assumed to be correct.
We used annotations that were created or in some way curated with human participation for gold standards.
There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
In the meantime, \citet{Plyusnin2019} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
\texttt{TODO\ DESCRIBE\ THEIR\ APPROACH}
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in \texttt{TODO}.

@@

\rowcolor{gray!6}   & GoldStandard & 1 & 11 & NA\\

@@

\rowcolor{gray!6}   &  & GoldStandard & 3.89 & 0.15 & 0.38 & 4.10 & 1,554 & 65 & 299 & 1,918 & 1 & 0 & 0 & 1\\

@@

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.384973 & 0.346840 & 0.191962 & 0.004446 & 0.006115 & 0.004811\\
\cmidrule{1-8}
 & GOMAP & 0.235407 & 0.348389 & 0.096186 & 0.035907 & 0.001639 & 0.001017\\

\rowcolor{gray!6}   & Gramene49 & 0.299075 & 0.359259 & 0.164630 & 0.055498 & 0.003230 & 0.001965\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.186238 & 0.347164 & 0.100965 & 0.014873 & 0.003058 & 0.000540\\
\cmidrule{1-8}
\rowcolor{gray!6}   & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}
\end{tablenotes}
\end{threeparttable}}
\end{table}
